WordRec Experiment

### 2019-08-27 Analysis/process.Rmd
first version journal

model_no_val <- as.data.frame(confint2(fit_children_no)) %>%
  mutate(val= Vr_ch_no, 
         model=1, 
         group = "children") %>%
  bind_rows(as.data.frame(confint2(fit_adults)) %>%
              mutate(val= Vr_ad_no, 
                     model=1, 
                     group = "adults"))

>>>>

model_no_val <- as.data.frame(confint2(fit_children_no)) %>%
  mutate(val= Vr_ch_no, 
         model=1, 
         group = "children") %>%
  bind_rows(as.data.frame(confint2(fit_adults_no)) %>%
              mutate(val= Vr_ad_no, 
                     model=1, 
                     group = "adults"))
